### 2020-03-24 korea.tex
k no more

>>>>

\section*{Abstract - 75 word limit; currently 70.}

On January 20, 2020, the first COVID-19 case was confirmed in South Korea.
As of March 18, 2020, 8,413 cases were confirmed but the number of cases has been consistently decreasing;
the reason for the decrease has been widely attributed to its intensive testing.
We report on the potential roles of social distancing in reducing transmission in South Korea.
Our analysis suggests that transmission may still persist in some regions.
